---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hydroapps

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of {hydroapps} is to to create apps for resource management in the context of hydrology monitoring and reporting. This package relies heavily on [USGS API](https://www.usgs.gov/products/data-and-tools/apis) and wouldn't be possible with out it (much thanks). However, this package is highly experimental and is used mostly by myself but I think it's worth sharing! That being said, Montana is really where I've focused time and energy; however, it wouldn't take much to add other states. Please enjoy and contributions are welcome!

## Installation

This is only in development right now.

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joshualerickson/hydroapps")
```

## Contributions

This package uses the [golem](https://github.com/ThinkR-open/golem) framework and thus uses modules to bring everything together. If you want to help contribute please be aware of this framework, i.e. see [here](https://engineering-shiny.org/golem.html) for more details. Other than that, contributions are welcomed!

## Basic Example

As of right now this only has one app running (streamstats)

```{r, eval=F}
run_app('streamstats')
```

