---
title: "Flood Frequency Report"
params: 
 set_author: "test" 
author: "`r params$set_author`"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: false
always_allow_html: true
---

```{r, echo=FALSE}

   culvert_size <- function(x) {
     ifelse(x < 11, "(24 in)", 
            ifelse(x >= 11 & x < 30,"(36 in)", 
                   ifelse(x >= 30 & x < 65,"(48 in)",
                          ifelse(x >= 65 & x <110,"(60 in)",
                                 ifelse(x >= 110 & x < 180,"(72 in)",
                                        ifelse(x >= 180 & x < 290,"(84 in)",
                                               ifelse(x >= 290 & x < 400,"(96 in)","(Bridge or Big Culvert!)")))))))}
   
 precipUpdate <- final_cul()$stats_usgs_cul %>% 
      dplyr::filter(stringr::str_detect(description, "Mean Annual Precip"))
    
    daUpdate <- final_cul()$stats_usgs_cul  %>% 
      dplyr::filter(stringr::str_detect(description, "Area that contributes flow to a point on a stream"))
    
    
    forUpdate <- final_cul()$stats_usgs_cul  %>% 
      dplyr::filter(stringr::str_detect(description, "Percentage of area covered by forest"))

togeth_sum_2 <- final_cul()$together_long %>% dplyr::filter(RI == 2, Method == "basin_char")%>% dplyr::summarise(mean = mean(value, na.rm = TRUE))

togeth_sum_10 <- final_cul()$together_long %>% dplyr::filter(RI == 10, Method == "basin_char")%>% dplyr::summarise(mean = mean(value, na.rm = TRUE))
    
          
togeth_sum_50 <- final_cul()$together_long %>% dplyr::filter(RI == 50, Method == "basin_char")%>% dplyr::summarise(mean = mean(value, na.rm = TRUE))


togeth_sum_100 <- final_cul()$together_long %>% dplyr::filter(RI == 100, Method == "basin_char") %>% dplyr::summarise(mean = mean(value, na.rm = TRUE))
```

## Introduction

This report is used to analyze the flood frequency and potential culvert sizing above <b>`r paste0(final_cul()$drain_name)`</b>. This is accomplished by generating geospatial parameters through free and opensource sofwares (FOSS) like USGS Stream Stats (Ries III et al., 2017) and R (Team, R, 2020). Furthermore, in field observations (bankfull- and active channel-width) can be added to the analysis as well. The parameters generated via USGS Stream Stats are many and depend on location, e.g. states, regions, etc. The geospatial parameters used by Omang, Parrett and Hull (1983) & Parrett and Johnson (2004) are mean annual precipitation, percentage of forest and drainage area, which are then used to calculate flood frequency using these parameters. In addition,  USGS Regional Regression Estimates (USGS RRE) will use the values and methods associated with specific location methods to generate peak flow estimates (Ries III et al., 2017). Furthermore, if the user has in-field measurements then Omang, Parrett and Hull (1983) & Parrett and Johnson (2004) take into account bankfull width and active channel width to generate flood frequency estimates. Finally, calculations for culvert size are recommended using flood frequency estimations and methods from American Iron, & Steel Institute (1983).

#### Quick Summary

 `r paste0("<b>Drainage Area: </b>", paste(daUpdate$value, " sq.mi"),
          "<br>","<b>Precipitation: </b>",paste(precipUpdate$value, " in."),
          "<br>","<b>Forest Cover: </b>",paste(forUpdate$value, " %"),
          "<br>", "<b>Basin Characteristics Avg 2 year: </b>", paste(scales::comma(togeth_sum_2$mean,2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"),"<li>",  "Culvert Size Recommended (2 yr): ", paste(culvert_size(togeth_sum_2$mean)), "</li>","<b>Basin Characteristics Avg 10 year: </b>", paste(scales::comma(togeth_sum_10$mean,2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"),"<li>",  "Culvert Size Recommended (10 yr): ", paste(culvert_size(togeth_sum_10$mean)), "</li>","<b>Basin Characteristics Avg 50 year: </b>", paste(scales::comma(togeth_sum_50$mean,2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"),"<li>",  "Culvert Size Recommended (50 yr): ", paste(culvert_size(togeth_sum_50$mean)), "</li>","<b>Basin Characteristics Avg 100 year: </b>", paste(scales::comma(togeth_sum_100$mean,2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"),"<br>","<li>",  "Culvert Size Recommended (100 yr): ", paste(culvert_size(togeth_sum_100$mean)), "</li>")`



# Catchment Characteristics


```{r, echo=FALSE, fig.align='center', fig.cap="Catchment Area (blue polygon) above selected Drain Point (red)", fig.pos="bottom"}
#knitr::include_graphics(final_cul()$customleaf)
```

The catchment characteristics are listed below in the table. Not all variables are used for flood frequency calculations but are added for the user to help capture the entire scope of the drainage. 

```{r, echo=FALSE}

final_cul()$stats_usgs_cul %>% dplyr::select(Description = description, Code = code, Unit = unit, Value = value) %>% kableExtra::kable(caption = paste0("Catchment Characteristics above selected point at ", final_cul()$drain_name)) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
```

This is the available flood frequency predictions for the catchment. 



```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center', fig.width=10, fig.height=5}
p1 <- final_cul()$together_long %>% ggplot(aes(RI, value, color = source)) + geom_point() + geom_line() +
  labs(x = "Return Interval", y = "Discharge (cfs)", title = paste0("Flood Frequency Estimates for ", final_cul()$drain_name)) + theme_bw() + facet_wrap(~Method)
plotly::ggplotly(p1)
```

## Flood Frequency Tables

Table below show the results from the calculations above using the USGS RRE, Omang, Parrett and Hull, and Parrett and Hull.

```{r, echo=FALSE}
final_cul()$together_long %>% dplyr::filter(RI %in% c(2,10,25,50,100)) %>% dplyr::select(`Return Interval` = ReturnInterval,Source = source, Method, Value = value, Size) %>% kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)
```




## References

American Iron, & Steel Institute. (1983). Handbook of steel drainage & highway construction products. American Iron and Steel Institute.

Omang, R. J., Parrett, C., & Hull, J. A. (1986). Methods for estimating magnitude and frequency of floods in Montana based on data through 1983 (No. 86-4027). US Geological Survey.

Parrett, C., & Johnson, D. R. (2004). Methods for estimating flood frequency in Montana based on data through water year 1998 (Vol. 3, No. 4308). US Department of the Interior, US Geological Survey.

Ries III, K. G., Newson, J. K., Smith, M. J., Guthrie, J. D., Steeves, P. A., Haluska, T. L., ... & Vraga, H. W. (2017). StreamStats, version 4 (No. 2017-3046). US Geological Survey.

Team, R. (2020). RStudio: Integrated development for R. RStudio Inc.(2015). Acknowledgements This work was supported by Fundação para a Ciência e Tecnologia (FCT), Azores.
