---
title: "Discharge Report for USGS Gauging Station: <br> <span style='color: black; font-size: 30px'> `r paste0(nwis_sites_df %>% dplyr::slice(n=1) %>% .$Station)`</span>"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: false
always_allow_html: true
---
<style>
@import url('https://fonts.googleapis.com/css2?family=Montserrat:wght@300&display=swap');

body {
    font-family: 'Montserrat', sans-serif;
    font-size: 12pt;
    line-height: 1.42857143;
    color: #333;
    background-color: #fff;
    overflow: auto;
}
</style>
```{r, include=F}
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))
library(dplyr)
library(ggplot2)
library(tidyr)
library(kableExtra)
library(scales)
thematic::thematic_on(font = 'Montserrat')
```

```{r echo=FALSE, warning=F, message=F, error=F}

one_row <- nwis_sites_df %>% slice(n=1)

month_station <- lubridate::as_date(Sys.Date()) %>% lubridate::month()

year_station <- lubridate::as_date(Sys.Date()) %>% lubridate::year()

day_station <- lubridate::as_date(Sys.Date()) %>% lubridate::day()

if(one_row$Station %in% 'Tobacco River near Eureka MT'){
  
  summary_stats <- nwis_sites_df  %>% 
  group_by(Station, month_abb) %>% 
  summarise(quantiles = quantile(Flow, probs = c(0.05, 0.1, 0.2, 0.25, 0.5,
                                                                  0.75,0.80, 0.90, 0.95), na.rm = TRUE),
            breaks =  c("p05_va", "p10_va", "p20_va", "p25_va", "p50_va", "p75_va",
                        "p80_va", "p90_va", "p95_va")) %>% 
  pivot_wider(values_from = quantiles, names_from = breaks)  %>% 
  right_join(nwis_sites_df, by = c("Station", "month_abb")) %>% 
  mutate(across(contains("_va"), round, 1)) %>% 
  ungroup() %>% 
  group_by(month_abb) %>% slice(n=1) %>% ungroup()%>% 
  mutate(across(p05_va:p95_va, round, 0))

  max_flow <- nwis_sites_df %>% 
  filter(month == month_station, day == day_station) %>% 
  slice_max(Flow) %>% slice(n = 1)
  
  max_dates <- nwis_sites_df %>% 
  filter(month == month_station, day == day_station) %>% 
    slice_max(Flow) %>% 
    pull(year)
  
  min_flow <- nwis_sites_df %>% 
  filter(month == month_station, day == day_station) %>% 
  slice_min(Flow) %>% slice(n = 1)
  
  min_dates <- nwis_sites_df %>% 
  filter(month == month_station, day == day_station) %>% 
    slice_min(Flow) %>% 
    pull(year)
  
  
  
dv_report <- nwis_sites_df %>% 
  group_by(Station, month_day) %>% 
  summarise(quantiles = quantile(Flow, probs = c(0.05, 0.1, 0.2, 0.25, 0.5,
                                                                  0.75,0.80, 0.90, 0.95), na.rm = TRUE),
            breaks =  c("p05_va", "p10_va", "p20_va", "p25_va", "p50_va", "p75_va",
                        "p80_va", "p90_va", "p95_va")) %>% 
  pivot_wider(values_from = quantiles, names_from = breaks)  %>% 
  right_join(nwis_sites_df, by = c("Station", "month_day")) %>% 
  mutate(across(contains("_va"), round, 0)) %>% 
  ungroup() %>% 
  group_by(Station, month_day) %>% 
    mutate(min_va = min_flow$Flow,
           max_va = max_flow$Flow,
           max_va_yr = stringr::str_c(max_dates, collapse = ', '),
           min_va_yr = stringr::str_c(min_dates, collapse = ', ')) %>% 
    ungroup() %>% 
  mutate(month_day = factor(month_day))
  
  hr_flow <- nwis_sites_df %>% wildlandhydRo::hourlyUSGS(days = 30) 
  
  u_hour <- hr_flow %>% mutate(Date = lubridate::as_date(date), 
        year = lubridate::year(Date), month = lubridate::month(Date), day = lubridate::day(Date), 
        month_day = str_c(month, day, sep = "-")) %>% group_by(Station, 
        month_day, Date) %>% summarise(current_daily_mean_flow = mean(value, 
        na.rm = TRUE)) %>% 
    ungroup() %>% 
    dplyr::left_join(dv_report %>% dplyr::select(dplyr::contains('_va'), Date), by = 'Date') %>% 
    dplyr::arrange(dplyr::desc(Date))
  
  u_hour[1,5:17] <- dv_report[1,] %>% dplyr::select(dplyr::contains('_va')) 
  
  cur_flow <- hr_flow %>% slice_max(date)
  
  hr_flow <- hr_flow %>%  mutate(Date = lubridate::as_date(date))
  
  dv_today <- u_hour %>% slice_max(Date)
  
  dv_30 <- u_hour %>% dplyr::semi_join(hr_flow, by = 'Date')
  
  
} else {
  
  usgs_st_m <- dataRetrieval::readNWISstat(one_row$site_no, 
                                         parameterCd = "00060", statType = "mean", 
                                         statReportType = "monthly")


summary_stats <- usgs_st_m %>% 
  dplyr::group_by(month = month_nu) %>% 
  summarize(p95_va = quantile(mean_va, probs = 0.95, na.rm = TRUE), 
            p90_va = quantile(mean_va, probs = 0.9, na.rm = TRUE), 
            p80_va = quantile(mean_va, probs = 0.8, na.rm = TRUE), 
            p75_va = quantile(mean_va, probs = 0.75, na.rm = TRUE), 
            p50_va = quantile(mean_va, probs = 0.5, na.rm = TRUE), 
            p25_va = quantile(mean_va, probs = 0.25, na.rm = TRUE), 
            p20_va = quantile(mean_va, probs = 0.2, na.rm = TRUE), 
            p10_va = quantile(mean_va, probs = 0.1, na.rm = TRUE), 
            p05_va = quantile(mean_va, probs = 0.05, na.rm = TRUE)) %>% 
  mutate(across(p05_va:p95_va, round, 0))

dv_report <- wildlandhydRo::reportUSGSdv(nwis_sites_df, days = 365) %>% dplyr::filter(!is.na(Date))


  hr_flow <- nwis_sites_df %>% wildlandhydRo::hourlyUSGS(days = 30)
  
  cur_flow <- hr_flow %>% slice_max(date)
  
  hr_flow <- hr_flow %>%  mutate(Date = lubridate::as_date(date))
  
  dv_today <- dv_report %>% slice_max(Date)
  
  dv_30 <- dv_report %>% dplyr::semi_join(hr_flow, by = 'Date')
 } 
joined_flows <- dplyr::left_join(hr_flow, dv_30, by = 'Date') %>% 
  dplyr::rename(`Current Flow` = 'value',`50th Percentile` = 'p50_va') %>% 
  group_by(Date) %>% mutate(`Current Flow` = mean(`Current Flow`, na.rm=T)) %>% 
  tidyr::pivot_longer(c(`Current Flow`,`50th Percentile`)) %>% ungroup()

last_flow <- joined_flows %>% group_by(name) %>% 
  summarise(last = dplyr::last(value))
    
  dv_today <- dv_today %>% mutate(current_monthly_mean_flow = nwis_sites_df %>% 
                                    filter(month == month_station, year == year_station) %>% pull(Flow) %>% mean())





```

This report provides numerous flow statistics at the USGS gauging station <b>`r paste0(one_row$Station)`</b>. This is accomplished by generating station statistics through opensource platforms like USGS {DataRetrieval} package (De Cicco et al., 2015) and R (Team, R, 2021). The idea is to give a brief summary of the station (summary stats).

<br>

::: {style="display: flex;"}
::: {style="flex-basis: 40%;"}
#### **Quick Summary**

`r paste0("<b>Station Name: </b>", paste(one_row$Station),           "<br>","<b>Drainage Area: </b>", paste(one_row$drainage_area, " sq.mi"),           "<br>","<b>Site #: </b>",paste(one_row$site_no), "<br>", "<b>Current Flow (instantaneous): </b>", paste(round(cur_flow$value, 2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"), "<br>", "<b>Current Flow (mean): </b>", paste(round(dv_today$current_daily_mean_flow, 2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"),"<br>", "<b>Current Monthly Flow (mean): </b>", paste(round(dv_today$current_monthly_mean_flow, 2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>"), "<br>", "<b>Minimum Flow: </b>", paste(round(dv_today$min_va,2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>", ' (', dv_today$min_va_yr, ')'), "<br>", "<b>Maximum Flow: </b>", paste(round(dv_today$max_va,2), " <sup>ft<sup>3</sup></sup>&frasl;<sub>s</sub>", ' (', dv_today$max_va_yr, ')'), "<br>", "<b>Period of Record: </b>", paste(min(nwis_sites_df$Date), ' to ', max(nwis_sites_df$Date)),
"<br>", "<b>Years with Data < 355 days: </b>", paste(' ', nwis_sites_df %>% dplyr::count(year) %>% dplyr::filter(n < 355) %>% tidyr::pivot_wider(names_from = n, values_from = year, names_glue = "count_{n}") %>% dplyr::mutate(years_missing = paste(unlist(.), collapse = ', ')) %>% dplyr::pull(years_missing)))`
:::

::: {style="flex-basis: 2%;"}
:::

::: {style="flex-basis: 68%;"}
```{r, echo=FALSE, warning=F, message=F, error=F}

if(!is.null(hr_flow)){
  dv_today <- dv_today %>% select(Date, p05_va:p95_va)%>% dplyr::rename(`5 %` = p05_va,
                                       `10 %` = p10_va,
                                       `20 %` = p20_va,
                                       `25 %` = p25_va,
                                       `50 %` = p50_va,
                                       `75 %` = p75_va,
                                       `80 %` = p80_va,
                                       `90 %` = p90_va,
                                       `95 %` = p95_va)
  dv_today_gt <- gt::gt(dv_today)

dv_today_gt %>%
  gt::tab_header(
    title = gt::md("**Percentiles:**"),
    subtitle = gt::md("**Daily Stats**")
  ) %>% gt::sub_missing(columns = c(-Date)) %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FF0000", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`5 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFA500", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`10 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFFF00", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`20 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color =  "#006400", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`25 %`, `50 %`, `75 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFFF00", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`80 %`)
    )
  ) %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFA500", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`90 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FF0000", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`95 %`)
    )
  ) %>% 
  gt::tab_options(table.border.top.style = 'none')

} else {
  
  dv_today <- dv_today %>% dplyr::mutate(`Month-Day` = paste(month_station, '-', day)) %>% 
    select(`Month-Day`, p05_va:p95_va)%>% dplyr::rename(`5 %` = p05_va,
                                       `10 %` = p10_va,
                                       `20 %` = p20_va,
                                       `25 %` = p25_va,
                                       `50 %` = p50_va,
                                       `75 %` = p75_va,
                                       `80 %` = p80_va,
                                       `90 %` = p90_va,
                                       `95 %` = p95_va)
  dv_today_gt <- gt::gt(dv_today)

dv_today_gt %>%
  gt::tab_header(
    title = gt::md("**Percentiles:**"),
    subtitle = gt::md("**Daily Stats**")
  ) %>% gt::sub_missing(columns = c(-`Month-Day`)) %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FF0000", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`5 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFA500", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`10 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFFF00", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`20 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color =  "#006400", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`25 %`, `50 %`, `75 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFFF00", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = `80 %`
    )
  ) %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFA500", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`90 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FF0000", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`95 %`)
    )
  ) %>% 
  gt::tab_options(table.border.top.style = 'none')
}

  mv_stats <- summary_stats %>% filter(month == month_station) %>% 
    dplyr::rename(Month = 'month') %>% 
    select(Month, p05_va:p95_va)%>% dplyr::rename(`5 %` = p05_va,
                                       `10 %` = p10_va,
                                       `20 %` = p20_va,
                                       `25 %` = p25_va,
                                       `50 %` = p50_va,
                                       `75 %` = p75_va,
                                       `80 %` = p80_va,
                                       `90 %` = p90_va,
                                       `95 %` = p95_va)
  mv_stats_gt <- gt::gt(mv_stats)

mv_stats_gt %>%
  gt::tab_header(
    title = '',
    subtitle = gt::md("**Monthly Stats**")
  ) %>% gt::sub_missing(columns = c(-Month)) %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FF0000", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`5 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFA500", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`10 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFFF00", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`20 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color =  "#006400", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`25 %`, `50 %`, `75 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFFF00", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = `80 %`
    )
  ) %>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FFA500", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`90 %`)
    )
  )%>% 
  gt::tab_style(
    style = list(
      gt::cell_fill(color = "#FF0000", alpha = 0.5)
      ),
    locations = gt::cells_body(
      columns = c(`95 %`)
    )
  ) %>% 
  gt::tab_options(table.border.top.style = 'none')

```
:::
:::
<br>
<center>
```{r echo=F, message = F, warning=F}
if(!is.null(hr_flow)){
g <- ggplot(data = joined_flows, aes(Date, value, color = name, linetype = name)) + 
  ggplot2::geom_line(size = 1, show.legend = F) + 
  scale_color_manual(values = c('forestgreen', 'black')) +
  ggplot2::theme_bw()  +
  ggplot2::theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10)) +
  ggplot2::labs(title = 'Last 30 days of flow',
                x = 'Date', y = 'Discharge (cfs)')
plotly::ggplotly(g)
} else {
  ggplot() + 
  ggplot2::geom_line() + 
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10)) +
  ggplot2::labs(title = 'Historic Data; No Current Flows',
                x = 'Date', y = 'Discharge (cfs)')
}

```
</center>
<br>
<center>
```{r, echo=FALSE, warning=FALSE,error=F, message = F, fig.align='center', fig.width=11}
if(dv_report[1,]$Station %in% 'Tobacco River near Eureka MT'){

  quart <- wildlandhydRo::plot_USGSdrought(usgs_ggplot_data_not_filtered(),
                                rolln = 1, 
                                startDate = max(usgs_ggplot_data_not_filtered()$Date)- 365,
                                endDate = max(usgs_ggplot_data_not_filtered()$Date)) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(size = 10),
        axis.text.y = ggplot2::element_text(size = 10)) +
    ggplot2::scale_y_continuous()
   plotly::ggplotly(quart)
 
} else {
  
 quart <- wildlandhydRo::plot_reportUSGS(dv_report) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(size = 10),
        axis.text.y = ggplot2::element_text(size = 10))+
    ggplot2::scale_y_continuous()
 plotly::ggplotly(quart)
}



```
</center>
<br>
<center>
```{r, echo=F,error=F, message=F}
month_abb <- data.frame(month = seq(1,12,1), month_abb = month.abb)
count_peak <- nwis_sites_df %>% wildlandhydRo::wyUSGS() %>% 
  mutate(month = lubridate::month(peak_dt)) %>% 
  dplyr::count(month) %>% filter(!is.na(month)) %>% 
  dplyr::full_join(month_abb, by = 'month') %>% 
  dplyr::mutate(n = ifelse(is.na(n), 0, n)) %>% 
  dplyr::mutate(month_abb = factor(month_abb, month.abb)) %>% 
  ggplot(aes(month_abb, n, fill = month_abb)) +
  ggplot2::geom_col(show.legend = F) +
  ggplot2::scale_fill_manual(values = c("#798E87","#8C8971","#A0845B","#B48046",
  "#C28340", "#C59758", "#C8AA70", "#CBBE88",  "#AEA77C", "#817A5D", "#554D3E","#29211F"))+
  labs(x = 'Month', y = '# of Peak Flows', title = 'Count of Peak Flows by Month') +
  ggplot2::theme_bw() +
    ggplot2::theme(axis.text.x = ggplot2::element_text(size = 10.5),
                   axis.title.x = ggplot2::element_text(size = 10.5),
        axis.text.y = ggplot2::element_text(size = 10.5),
        strip.text = ggplot2::element_text(size = 10.5),
        plot.title = ggplot2::element_text(size = 12.5),
        axis.title.y = ggplot2::element_text(size = 10.5),
        plot.subtitle = ggplot2::element_text(size = 10.5),
        legend.position = 'none')

plotly::ggplotly(count_peak)
```
</center>
<br>
<br>
<center>
## Zonal Stats

```{r, echo=FALSE, message=FALSE, error=FALSE,warning=F, fig.align='center'}
basin_sf <- nwis_sites_df %>%
  dplyr::slice_head(n=1) %>% 
  sf::st_as_sf(coords = c('long', 'lat'))
basin <- basin_sf %>% wildlandhydRo::get_Basin()
basin_stats <- wildlandhydRo::get_BasinStats(basin) %>% dplyr::select(-Date, -c(year:month_abb)) 

meta <- nhdplusTools::discover_nldi_characteristics('total') %>% .[['total']]

meta_df <- meta %>% dplyr::left_join(basin_stats %>% 
                                       tidyr::pivot_longer(dplyr::starts_with('TOT_'), names_to = 'characteristic_id'), by = 'characteristic_id')

leaf <- base_map() %>% 
  leaflet::addCircleMarkers(data = basin_sf, color = 'red') %>% 
  leaflet::addPolygons(data = basin_stats)
  #                      popup = leafpop::popupTable(basin_stats %>% 
  # dplyr::rename_with(~stringr::str_remove(., 'TOT_'), starts_with('TOT_')) %>% 
  #                                                    dplyr::filter(stringr::str_detect('BFI|TWI'))))
leaf
```


```{r, echo=FALSE, message=FALSE, error=FALSE,warning=F}

DT::datatable(meta_df%>% 
  dplyr::mutate(characteristic_id = stringr::str_remove(characteristic_id, 'TOT_')) %>% 
    dplyr::select(characteristic_id, characteristic_description, value, units))
```
</center>
## References

De Cicco, L.A., Hirsch, R.M., Lorenz, D., Watkins, W.D., 2018, dataRetrieval: R packages for discovering and retrieving water data available from Federal hydrologic web services, <doi:10.5066/P9X4L3GE>  

R Core Team (2021). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.  

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>